Manuscript

### 2014-10-14 inst/simulation/manuscript.Rmd
...

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  return(credibilityIntervals)  
}

>>>>

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  return(credibilityIntervals)  
}
